biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2024-11-21 paper/PaperTRA/PaperTRA_rev2.Rmd
add proper basemap caption on TRA Springer paper

```{r map1, out.width="60%", fig.cap="Interfaces and lines considered, by transport mode, in the Lisbon metropolitan area", fig.align='center', fig.pos="h"}
knitr::include_graphics("img/map1.png", error = FALSE)
```

>>>>

```{r map1, out.width="60%", fig.cap="Interfaces and lines considered, by transport mode, in the Lisbon metropolitan area. Author created map, using the mapview R package, with OpenStreetMap CARTO basemap.", fig.align='center', fig.pos="h"}
knitr::include_graphics("img/map1.png", error = FALSE)
```

### 2024-11-21 paper/PaperTRA/PaperTRA_rev2.tex
add proper basemap caption on TRA Springer paper

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{modeling-origin-destination-trips}{%
\subsection{Modeling Origin-Destination
trips}\label{modeling-origin-destination-trips}}

@@

\hypertarget{modeling-intermodality}{%
\subsection{Modeling intermodality}\label{modeling-intermodality}}

@@

\caption{Interfaces and lines considered, by transport mode, in the Lisbon metropolitan area}\label{fig:map1}
\end{figure}

@@

\hypertarget{assessing-socio-environmental-benefits}{%
\subsection{Assessing socio-environmental
benefits}\label{assessing-socio-environmental-benefits}}

@@

\hypertarget{results-and-discussion}{%
\section{Results and Discussion}\label{results-and-discussion}}

@@

\hypertarget{acknowledgements.}{%
\subsubsection*{Acknowledgements.}\label{acknowledgements.}}
\addcontentsline{toc}{subsubsection}{Acknowledgements.}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-MARTENS2007326}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Martens, K.: Promoting bike-and-ride: The dutch
experience. Transportation Research Part A: Policy and Practice. 41,
326--338 (2007).
https://doi.org/\href{https://doi.org/10.1016/j.tra.2006.09.010}{10.1016/j.tra.2006.09.010}.}

\leavevmode\vadjust pre{\hypertarget{ref-RIETVELD200071}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Rietveld, P.: The accessibility of railway stations: The
role of the bicycle in the netherlands. Transportation Research Part D:
Transport and Environment. 5, 71--75 (2000).
https://doi.org/\href{https://doi.org/10.1016/S1361-9209(99)00019-X}{10.1016/S1361-9209(99)00019-X}.}

\leavevmode\vadjust pre{\hypertarget{ref-IMOB}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{INE:
\href{https://www.ine.pt/xportal/xmain?xpid=INE\&xpgid=ine_publicacoes\&PUBLICACOESpub_boui=349495406\&PUBLICACOESmodo=2\&xlang=pt}{Mobilidade
e funcionalidade do território nas {Áreas Metropolitanas do Porto e de
Lisboa}: 2017}. {Instituto National de Estatística}, Lisboa (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-felix2023}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Félix, R., Lovelace, R., Moura, F.: {biclaR - Ferramenta
de apoio ao planeamento da rede ciclável na área metropolitana de
Lisboa}, \url{https://biclar.tmlmobilidade.pt}, (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-lovelace2017}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Lovelace, R., Goodman, A., Aldred, R., Berkoff, N.,
Abbas, A., Woodcock, J.: The Propensity to Cycle Tool: An open source
online system for sustainable transport planning. Journal of Transport
and Land Use. 10, (2017).
https://doi.org/\href{https://doi.org/10.5198/jtlu.2016.862}{10.5198/jtlu.2016.862}.}

\leavevmode\vadjust pre{\hypertarget{ref-Lovelace2022Jittering}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Lovelace, R., Félix, R., Carlino, D.: Jittering: A
computationally efficient method for generating realistic route networks
from origin-destination data. Findings. (2022).
https://doi.org/\href{https://doi.org/10.32866/001c.33873}{10.32866/001c.33873}.}

\leavevmode\vadjust pre{\hypertarget{ref-r5r}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Pereira, R.H.M., Saraiva, M., Herszenhut, D., Braga,
C.K.V., Conway, M.W.: r5r: Rapid realistic routing on multimodal
transport networks with R5 in r. Findings. (2021).
https://doi.org/\href{https://doi.org/10.32866/001c.21262}{10.32866/001c.21262}.}

\leavevmode\vadjust pre{\hypertarget{ref-HEAT}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Kahlmeier, S., Götschi, T., Cavill, N., Castro
Fernandez, A., Brand, C., Rojas Rueda, D., Woodcock, J., Kelly, P.,
Lieb, C., Oja, P., others:
\href{https://www.euro.who.int/__data/assets/pdf_file/0010/352963/Heat.pdf}{Health
economic assessment tool ({HEAT}) for walking and for cycling: Methods
and user guide on physical activity, air pollution, injuries and carbon
impact assessments}. (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-COPERT}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Ntziachristos, L., Samaras, Z.: {EMEP/EEA} air pollutant
emission inventory guidebook 2019,
\url{https://www.emisia.com/utilities/copert/documentation/}, (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-EuropeanCommission2014}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Sartori, D., Catalano, G., Genco, M., Pancotti, C.,
Sirtori, E., Vignetti, S., Del Bo, C.:
\href{https://ec.europa.eu/regional_policy/sources/docgener/studies/pdf/cba_guide.pdf}{Guide
to cost-benefit analysis of investment projects. Economic apraisal tool
for cohesion policy 2014-2020}. {European Commission - Directorate
General for Regional and Urban Policy} (2014).}

>>>>

% Pandoc citation processing
%From Pandoc 3.1.8
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\section{Introduction}\label{introduction}

@@

\section{Methods}\label{methods}

\subsection{Modeling Origin-Destination
trips}\label{modeling-origin-destination-trips}

@@

\subsection{Modeling intermodality}\label{modeling-intermodality}

@@

\caption{Interfaces and lines considered, by transport mode, in the Lisbon metropolitan area. Author created map, using the mapview R package, with OpenStreetMap CARTO basemap.}\label{fig:map1}
\end{figure}

@@

\subsection{Assessing socio-environmental
benefits}\label{assessing-socio-environmental-benefits}

@@

\section{Results and Discussion}\label{results-and-discussion}

@@

\subsubsection*{Acknowledgements.}\label{acknowledgements.}
\addcontentsline{toc}{subsubsection}{Acknowledgements.}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-MARTENS2007326}
\CSLLeftMargin{1. }%
\CSLRightInline{Martens, K.: Promoting bike-and-ride: The dutch
experience. Transportation Research Part A: Policy and Practice. 41,
326--338 (2007).
https://doi.org/\href{https://doi.org/10.1016/j.tra.2006.09.010}{10.1016/j.tra.2006.09.010}.}

\bibitem[\citeproctext]{ref-RIETVELD200071}
\CSLLeftMargin{2. }%
\CSLRightInline{Rietveld, P.: The accessibility of railway stations: The
role of the bicycle in the netherlands. Transportation Research Part D:
Transport and Environment. 5, 71--75 (2000).
https://doi.org/\href{https://doi.org/10.1016/S1361-9209(99)00019-X}{10.1016/S1361-9209(99)00019-X}.}

\bibitem[\citeproctext]{ref-IMOB}
\CSLLeftMargin{3. }%
\CSLRightInline{INE:
\href{https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=349495406&PUBLICACOESmodo=2&xlang=pt}{Mobilidade
e funcionalidade do território nas {Áreas Metropolitanas do Porto e de
Lisboa}: 2017}. {Instituto National de Estatística}, Lisboa (2018).}

\bibitem[\citeproctext]{ref-felix2023}
\CSLLeftMargin{4. }%
\CSLRightInline{Félix, R., Lovelace, R., Moura, F.: {biclaR - Ferramenta
de apoio ao planeamento da rede ciclável na área metropolitana de
Lisboa}, \url{https://biclar.tmlmobilidade.pt}, (2022).}

\bibitem[\citeproctext]{ref-lovelace2017}
\CSLLeftMargin{5. }%
\CSLRightInline{Lovelace, R., Goodman, A., Aldred, R., Berkoff, N.,
Abbas, A., Woodcock, J.: The Propensity to Cycle Tool: An open source
online system for sustainable transport planning. Journal of Transport
and Land Use. 10, (2017).
https://doi.org/\href{https://doi.org/10.5198/jtlu.2016.862}{10.5198/jtlu.2016.862}.}

\bibitem[\citeproctext]{ref-Lovelace2022Jittering}
\CSLLeftMargin{6. }%
\CSLRightInline{Lovelace, R., Félix, R., Carlino, D.: Jittering: A
computationally efficient method for generating realistic route networks
from origin-destination data. Findings. (2022).
https://doi.org/\href{https://doi.org/10.32866/001c.33873}{10.32866/001c.33873}.}

\bibitem[\citeproctext]{ref-r5r}
\CSLLeftMargin{7. }%
\CSLRightInline{Pereira, R.H.M., Saraiva, M., Herszenhut, D., Braga,
C.K.V., Conway, M.W.: r5r: Rapid realistic routing on multimodal
transport networks with R5 in r. Findings. (2021).
https://doi.org/\href{https://doi.org/10.32866/001c.21262}{10.32866/001c.21262}.}

\bibitem[\citeproctext]{ref-HEAT}
\CSLLeftMargin{8. }%
\CSLRightInline{Kahlmeier, S., Götschi, T., Cavill, N., Castro
Fernandez, A., Brand, C., Rojas Rueda, D., Woodcock, J., Kelly, P.,
Lieb, C., Oja, P., others:
\href{https://www.euro.who.int/__data/assets/pdf_file/0010/352963/Heat.pdf}{Health
economic assessment tool ({HEAT}) for walking and for cycling: Methods
and user guide on physical activity, air pollution, injuries and carbon
impact assessments}. (2017).}

\bibitem[\citeproctext]{ref-COPERT}
\CSLLeftMargin{9. }%
\CSLRightInline{Ntziachristos, L., Samaras, Z.: {EMEP/EEA} air pollutant
emission inventory guidebook 2019,
\url{https://www.emisia.com/utilities/copert/documentation/}, (2020).}

\bibitem[\citeproctext]{ref-EuropeanCommission2014}
\CSLLeftMargin{10. }%
\CSLRightInline{Sartori, D., Catalano, G., Genco, M., Pancotti, C.,
Sirtori, E., Vignetti, S., Del Bo, C.:
\href{https://ec.europa.eu/regional_policy/sources/docgener/studies/pdf/cba_guide.pdf}{Guide
to cost-benefit analysis of investment projects. Economic apraisal tool
for cohesion policy 2014-2020}. {European Commission - Directorate
General for Regional and Urban Policy} (2014).}
